formula1

### 2019-12-16 inst/formula1.Rmd
all years 2014-2017

this script takes about a minute to run.  It creates hyper2 objects
`F1_2014` through `F1_2017`, which are the likelihood functions for
the F1 results table for each of the years.

Function `F1_likelihood()` is defined here; this creates objects such as
`F1_2017` by processing `formula1_2017.txt`.

At the end of the script, hyper2 object `F1_total` is created, which
is a likelihood function for all four years' data.  This object is
called 'formula1' in the package.  File `F1_allyears.R` is functionally
identical but uses slightly different R idiom.

>>>>

## All years data

We will consider four years data:

```{r,fouryearsdata}
F1_2014 <- "formula1_2014.txt" %>% read.table(header=TRUE) %>% F1_likelihood
F1_2015 <- "formula1_2015.txt" %>% read.table(header=TRUE) %>% F1_likelihood
F1_2016 <- "formula1_2016.txt" %>% read.table(header=TRUE) %>% F1_likelihood
F1_2017 <- "formula1_2017.txt" %>% read.table(header=TRUE) %>% F1_likelihood
a <- list(F1_2014, F1_2015, F1_2016, F1_2017)
alldrivers <- all_pnames(a)

F1_total <- hyper2(pnames=alldrivers)

F1_total %<>% add(change_pnames(F1_2014,alldrivers)) 
F1_total %<>% add(change_pnames(F1_2015,alldrivers)) 
F1_total %<>% add(change_pnames(F1_2016,alldrivers)) 
F1_total %<>% add(change_pnames(F1_2017,alldrivers))

(mallyears <- maxp(F1_total))
```

and the plot:

```{r,allyearplot,fig.height=7}
dotchart(mallyears,pch=16,main='Formula 1, 2014-7')
```
